Learning CNN filters from user-drawn image markers for coconut-tree image classification

### 2020-07-24 IEEE-GRSL-Response-Letter.tex

\rwr{1} we identified cohesive groups of images from each class and selected two representative images from each class to draw markers.}

\ans We have changed the way to explain the choice of representative images from each class to draw markers. The new Figure 3 also helps in that explanation. \eans

\rwr{1} We have not investigated the impact of placing markers on a higher number of images and network architecture optimization procedures yet.

\ans Thanks a lot for the suggestion related to this sentence. The sentence has been removed, and we have added experiments with an increasing number of images for marker selection. The results, shown in Table II, demonstrate that FLIM is not negatively affected by choice of marker pixels in a higher number of images. On the other hand, we consider these results inconclusive. We believe it is possible to assist the user in visually identifying relevant images and regions in those images for marker selection. However, this point requires further investigation and suitable image processing with data visualization.   \eans

### 2020-07-24 IEEE-GRSL-Response-Letter.tex

\rwr{1} We have not investigated the impact of placing markers on a higher number of images and network architecture optimization procedures yet.

\ans Thanks a lot for the suggestion related to this sentence. The sentence has been removed, and we have added experiments with an increasing number of images for marker selection. The results, shown in Table II, demonstrate that FLIM is not negatively affected by choice of marker pixels in a higher number of images. On the other hand, we consider these results inconclusive. We believe it is possible to assist the user in visually identifying relevant images and regions in those images for marker selection. However, this point requires further investigation and suitable image processing with data visualization.   \eans

\rwr{1} We use Pytorch to implement our feature extractor and the MLP classifier.

\ans MLP stands for multi-layer perceptron and it was defined in the first paragraph of Section II. We have redefined it again in Section III. We have also included the specifications of the machine used for the experiments in the beginning of the second paragraph in Section III. \eans

### 2020-07-24 IEEE-GRSL-Response-Letter.tex

\rwr{1} We have not investigated the impact of placing markers on a higher number of images and network architecture optimization procedures yet.

\ans Thanks a lot for the suggestion related to this sentence. The sentence has been removed, and we have added experiments with an increasing number of images for marker selection. The results, shown in Table II, demonstrate that FLIM is not negatively affected by choice of marker pixels in a higher number of images. On the other hand, we consider these results inconclusive. We believe it is possible to assist the user in visually identifying relevant images and regions in those images for marker selection. However, this point requires further investigation and suitable image processing with data visualization.   \eans

\rwr{1} We use Pytorch to implement our feature extractor and the MLP classifier.

\ans MLP stands for a multi-layer perceptron, and it was defined in the first paragraph of Section II. We have redefined it again in Section III. We have also added the machine used for the experiments at the beginning of the second paragraph in Section III. \eans

@@

\rwr{1} Caption of the previous Fig. 3 (Fig. 4 now): Markers used for training in image regions with (first column) and without (second column) a coconut tree.

\ans Thanks, we have fixed that indicating which marker color is used to indicate each class. 
\eans

@@

\rwr{1}{By comparing ``FLIM+MLP'' with VGG, one can observe that FLIM reduces the number of required training images. Finally, the comparison between ``FLIM+MLP'' and VGG-FT demonstrates that FLIM can provide competitive results using a considerably more simplified architecture than  VGG-FT.}

\ans Thanks, we have removed `` '' around the names of the methods.\eans

@@

\rwr{2} This paper presents a new feature learning approach that can be used to reduce the number of required images to train a deep neural network. It introduces a novel way to estimate filter weights for the convolutional layers using user-drawn markers in a few training images. The need for a large number of labeled input samples is a very well known and important problem for many CNN models and the proposed solution seems to be promising but the paper has some presentation and methodological problems that must be addressed.

\ans Thanks for the comments. We have improved the experiments in Section III and the presentation of the work in several parts of the text. 
\eans

@@

\rwr{2} Pg. 5 - Line 6: An error in the paper title is something that should be avoided at all costs as it is very confusing for the reader.  "...User-drawn Image MAKERS..." ??? The first word of the introduction is also wrong: "DePP learning"? Overall, there are not many language errors, but a proof-reading is highly recommended

\ans Thanks. We have fixed them and revised the entire text to avoid typos. \eans

### 2020-07-24 main.tex
Updates from Overleaf

\textcolor{red}{Pytorch was chosen to implement FLIM and MLP, being SVM the linear model available in scikit-learn with $C=0.01$~\cite{fan2008liblinear, scikit-learn}. We trained MLP for $40$ epochs and the whole network for $60$ epochs with a batch size of $64$. We used a learning rate of $0.0001$, a weight decay of $0.001$, and we updated the learning rate by a factor of $0.1$ at every $5$ epochs after epoch 30. VGG and VGG-FT were trained for $95$ epochs with a batch size of $64$, a learning rate of $0.001$, weight decay of $0.001$, and we updated the learning rate by a factor of $0.1$ at every $5$ epochs after the model achieved accuracy $0.95$.}

>>>>

\textcolor{red}{Pytorch was chosen to implement FLIM and MLP, being SVM the linear model available in scikit-learn with~${C=0.01}$~\cite{fan2008liblinear, scikit-learn}. We trained MLP for $40$ epochs and the whole network for $60$ epochs with a batch size of $64$. We used a learning rate of $0.0001$, a weight decay of $0.001$, and we updated the learning rate by a factor of $0.1$ at every $5$ epochs after epoch 30. VGG and VGG-FT were trained for $95$ epochs with a batch size of $64$, a learning rate of $0.001$, weight decay of $0.001$, and we updated the learning rate by a factor of $0.1$ at every $5$ epochs after the model achieved accuracy $0.95$.}
